Senior Technical Support Analyst, Pearson – Centennial, CO
June 2015 – Present
Actively develop tools and automation library in PowerShell. Focus is on account management, application recovery, and server maintenance.
Led internal training classes on programming and automation in PowerShell.
Built synthetic monitoring tests using Selenium WebDriver (Javascript) for use in New Relic.
Managed monitoring in: New Relic, AppDynamics , ipMonitor, SiteScope, Zabbix, Zenoss, Selenium, ActiveXperts
Performed access reviews for internal support accounts in accordance with Risk Management requirements.
Interfaced with other teams to on-board their applications/servers to be monitored by the Command Center.
Thoroughly documented technical tasks and business processes.

Technical Support Analyst, Pearson – Centennial, CO
June 2014 – June 2015
Automated common tasks with PowerShell. Created a central & standardized library of cmdlets. Managed development using Git for repository management, Pester for unit testing, and Jira for tracking feature/bugfix/release work.
Trained colleagues on programming concepts, how to write reusable PowerShell, and development tools.
Planned and executed server migration and redistribution of a critical monitoring system (ActiveXperts). Required coordination with counterparts in Sri Lanka.
Created PowerShell script to automate account creation and credential distribution, saving 40 work-hours per quarter.
Assisted incident managers during high-priority incidents (ITIL P1/P2) by contacting necessary teams and performing system diagnostics.

PC Support Specialist, Concordia College - Moorhead, MN
May 2012 – June 2014
Developed a flexible, automated, and fault-tolerant scripted framework for imaging workstations using the Dell KACE 2100 which reduced technician workload.
Redesigned and tested domain-wide GPO settings to increase consistency and security of workstation configurations.
Analyzed current processes and began automating management tasks using both scripting and existing software. Documented the usage and maintenance of the resulting automation process.
Prototyped and documented a centralized log management system using the ELK stack (Elasticsearch, Logstash, Kibana) on CentOS 6.5 to provide easier searching and trend analysis of system logs.
Audited security posture of workstation images and took steps to correct insecure settings.
Was responsible for creating, updating, and organizing documentation on internally used knowledge base.
Received cross-training in the deployment and management of Red Hat Enterprise Linux 6.
Provided troubleshooting support for LAN/WAN issues on client machines.
Extensive experience in troubleshooting and replacement of hardware on client desktops and laptops.
Provided in-depth technical support to end-users of both Mac OSX and Windows XP/7 systems.

Student Manager, Concordia College - Moorhead, MN
May 2010 – May 2012
Evaluated strategic direction of IT help desk services.  Created, successfully promoted, and executed a plan to increase efficiency and effectiveness of IT support operations.
Responsible for the personnel management of 11 student technicians.  Provided daily work direction and was responsible for biannual performance reviews.
Created a student employee training program to ensure the continuity and stability of the department’s policies and procedures in an environment of high employee turn-over.

Student Technician, Concordia College - Moorhead, MN
Fall 2008 – Summer 2010
Provided tier 1 technical support for Windows and Mac systems.
Worked with senior technicians to address higher tier technical issues.
Updated and expanded current documentation to include new responsibilities the student technician staff had be granted.

Intern Web Designer, Medtronic Science and Technology - Fridley, MN
Summer 2007
Researched, tested, and began implementing a new structuring style to an internal website’s codebase to promote code reuse and reduce maintenance.
Worked on both front end graphic layout and back-end data processing.
Learned necessary coding languages (Coldfusion 7, javascript) through self-study and minimal tutoring from peers.