\cventry
	{Senior Technical Support Analyst} % Job title
	{Pearson} % Organization
	{Centennial, CO} % Location
	{June 2015 – Present} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Actively develop custom tools and automation library in PowerShell for internal use in alignment with software engineering best practices.}
			\item {Organized and led internal training classes on programming and automation in PowerShell.}
			\item {Utilize Vagrant for building test environments.}
			\item {Built synthetic monitoring tests using Selenium WebDriver (JavaScript) for use in New Relic.}
			\item {Manage monitoring in: New Relic, AppDynamics, and Zabbix, among others.}
			\item {Planned and wrote operational and instructional documents involving technical tasks and business processes.}
			\item {Effectively communicate technical specifications/instructions to non-technical audiences.}
		\end{cvitems}
	}

\cventry
	{Technical Support Analyst} % Job title
	{Pearson} % Organization
	{Centennial, CO} % Location
	{June 2014 – June 2015} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Automated repetitive tasks with PowerShell. Created a standardized library of cmdlets. Managed development using Git for repository management, Pester for unit testing, and Jira for tracking features/bugfixes/release management.}
			\item {Trained colleagues on programming concepts, how to write reusable PowerShell, and development tools.}
			\item {Created PowerShell to automate account creation and credential distribution, saving 40 work-hours per quarter.}
			\item {Planned, coordinated, and performed server migration and redistribution of a critical monitoring system (ActiveXperts) with Sri Lankan counterparts.}
			\item {Perform quarterly internal account audits.}
			\item {Assisted incident managers during high-priority incidents (ITIL P1/P2) by contacting necessary teams and performing system diagnostics.}
		\end{cvitems}
	}

\cventry
	{PC Support Specialist} % Job title
	{Concordia College} % Organization
	{Moorhead, MN} % Location
	{May 2012 – June 2014} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Developed a flexible, automated, and fault-tolerant scripted framework for imaging workstations using the Dell KACE 2100 which reduced technician workload by an average of 1 hour per deployment.}
			\item {Redesigned and tested domain-wide GPO settings to increase consistency and security of workstation configurations.}
			\item {Analyzed current processes and began automating management tasks using both scripting and existing software. Documented the usage and maintenance of the resulting automation process.}
			\item {Prototyped and documented a centralized log management system using the ELK stack (Elasticsearch, Logstash, Kibana) on CentOS 6.5 to provide easier searching and trend analysis of system logs.}
			\item {Audited security posture of workstation images and took steps to correct insecure settings.}
			\item {Responsible for creating, updating, and organizing documentation on internally used knowledge base.}
			\item {Provided technical support for end user machines.}
		\end{cvitems}
	}

\cventry
	{Student Manager} % Job title
	{Concordia College} % Organization
	{Moorhead, MN} % Location
	{May 2010 – May 2012} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Evaluated strategic direction of IT help desk services.  Created, successfully promoted, and executed a plan to increase efficiency and effectiveness of IT support operations.}
			\item {Responsible for the personnel management of 11 student technicians.  Provided daily work direction and was responsible for biannual performance reviews.}
			\item {Developed and managed a student employee training program to ensure the continuity and stability of the department’s policies and procedures in an environment of high employee turn-over.}
		\end{cvitems}
	}

\cventry
	{Student Technician} % Job title
	{Concordia College} % Organization
	{Moorhead, MN} % Location
	{Fall 2008 – Summer 2010} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Provided tier 1 technical support for Windows and Mac systems.}
			\item {Worked with senior technicians to address higher-tier technical issues.}
			\item {Updated and expanded documentation to include new responsibilities that the student technician staff had been granted.}
		\end{cvitems}
	}

\cventry
	{Intern Web Designer} % Job title
	{Medtronic, Science and Technology} % Organization
	{Fridley, MN} % Location
	{Summer 2007} % Date(s)
	{
	  	\begin{cvitems} % Description(s) of tasks/responsibilities
	        \item {Researched, tested, and began implementing a new structuring style to an internal website’s codebase to promote code reuse and reduce maintenance.}
			\item {Worked on both front-end graphic layout and back-end data processing.}
			\item {Learned necessary coding languages (Coldfusion 7, JavaScript) through self-study and minimal tutoring from peers.}
		\end{cvitems}
	}